Language Bias in a Multilingual Tweet Corpus

### 2018-06-29 paper.tex
Aestetics
Topic titles
Minor

The tweets were written by \hl{41\,170} users. We refer to a user who produced at least 50 tweets as an \textit{active user}. There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1,196,558} (\hl{86.6\%}) tweets in total.

@@

The topics are:\footnotemark{}
\footnotetext{The topic file is available as \sfile{topics.json.txt}.}
\begin{itemize}
\item \texttt{LV016:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
\item \texttt{LV005:} \textbf{Ice hockey} \ Ice hockey.
\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV009:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
\item \texttt{LV001:} \textbf{Winter} \ Winter, snow and cold weather.
\item \texttt{LV015:} \textbf{May 4} \ The Restoration of Independence Day.
\item \texttt{LV011:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8). It is also honored as the Victory Day on May 9. The Europe Day is observed on May 9. Tweets about any of the three events are relevant.
\item \texttt{LV010:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
\item \texttt{LV014:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
\item \texttt{LV013:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
\item \texttt{LV006:} \textbf{Christmas} \ Christmas.
\item \texttt{LV007:} \textbf{New Year} \ New Year.
\item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
\item \texttt{LV012:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
\end{itemize}

@@

In case of Christmas, we see unexpected activity in March which is due to the discussion of making the Orthodox Christmas a public holiday in Parliament. This topic exhibits some cultural differences and language use. Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated. It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring, November 11 became a public holiday, thus a spike in activity.  Other event-related topics (May 4, May 8-9, etc.) behave similarly: their activity peaks during the event.

>>>>

The tweets were written by \hl{41\,170} users. We refer to a user who produced at least 50 tweets as an \textit{active user}. There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1\,196\,558} (\hl{86.6\%}) tweets in total.

@@

The topics are:\footnotemark{}
\footnotetext{The topic file is available as \sfile{topics.json.txt}.}
\begin{itemize}
\item \texttt{LV016:} \textbf{Latvia 100} \ The Centennial Celebration of the Republic of Latvia.
\item \texttt{LV005:} \textbf{Ice Hockey} \ Ice hockey.
\item \texttt{LV003:} \textbf{Refugees} \ Refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV009:} \textbf{Brexit} \ Withdrawal of the United Kingdom from the European Union known as Brexit.
\item \texttt{LV002:} \textbf{The Chronicles of Melanie} \ Mel\=anijas Hronika (The Chronicles of Melanie) is a Latvian movie that was selected for the Foreign-Language Category for Oscars.
\item \texttt{LV004:} \textbf{Blizzard of Souls} \ A Latvian movie Dv\=ese\c{l}u Putenis (Blizzard of Souls) that is in production by the time of writing.
\item \texttt{LV001:} \textbf{Winter} \ Winter, snow and cold weather.
\item \texttt{LV015:} \textbf{May 4} \ The Restoration of Independence Day.
\item \texttt{LV011:} \textbf{May 8-9} \ Remembrance of the end of Word War II (May 8). It is also honored as the Victory Day on May 9. The Europe Day is observed on May 9. Tweets about any of the three events are relevant.
\item \texttt{LV010:} \textbf{Midsummer} \ Midsummer celebration on June 23-24.
\item \texttt{LV014:} \textbf{November 11} \ A memorial day for soldiers who fought for the independence of Latvia.
\item \texttt{LV013:} \textbf{November 18} \ Proclamation Day of the Republic of Latvia.
\item \texttt{LV006:} \textbf{Christmas} \ Christmas.
\item \texttt{LV007:} \textbf{New Year} \ New Year.
\item \texttt{LV008:} \textbf{Olympics} \ The Olympic games and the Latvian team.
\item \texttt{LV012:} \textbf{March 16} \ Remembrance Day of the Latvian legionnaires.\footnotemark{}
\end{itemize}

@@

In case of Christmas, we see unexpected activity in March which is due to the discussion of making the Orthodox Christmas a public holiday in Parliament. This topic exhibits some cultural differences and language use. Tweets in Latvian peak during Advent and Christmas in December, tweets in Russian reach maximum both in December and early January when Orthodox Christmas are celebrated. It is worth noting that during the discussion whether Orthodox Christmas should be a public holiday, it sometimes was referred as ``Russian Christmas.'' In spring 2018, there was a discussion to make November 11 a public holiday, thus a spike in activity. Other event-related topics (May 4, May 8-9, etc.) behave similarly: their activity peaks during the event.
